---
title: "Dashboard Project Name Here" 
output:
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---
    
    
```{r setup, include=FALSE, warning=FALSE}

# Flexdashboard documentation--- https://rmarkdown.rstudio.com/flexdashboard/index.html

#----------- A Few Notes
#   - While everything can be included in this RMD, it's usually better to separate the data processing into its own script
#   - This template is setup to include interactive Shiny elements
#   - This template includes 2 tabs
#            - 1) An about page for study description and links to key personnel (or anything else you like)
#            - 2) A cohort page with place holder elements
#   - There are a couple of examples of Shiny inputs. 
#            - To access the gender filter value in this dashboard use input$gender
#            - To use a Shiny input, you need to wrap it in a "render" call. (ex. renderTable({}))
#


#---------------------------------- Packages ----------------------------------------
library(flexdashboard)
library(tidyverse)
library(shiny)
library(knitr)

```



```{r data, include=FALSE}

#---------------------------------- Data Import ----------------------------------------

#some fake data
id <- c(1,2,3,4,5,6,7,8,9,10,11,12)
gender <- c("Male", "Female", "Female", "Female", "Male", "Female", "Female", "Female", "Female", "Female", "Male", "Male")
site <- c("ARZ", "ARZ", "RST", "ARZ", "ARZ", "FLA", "FLA", "ARZ", "RST", "ARZ", "ARZ", "FLA")
mydata<- data.frame(id, gender, site)
mydata$id <- as.character(mydata$id)
#---------------------------------- Data Transformation --------------------------------



```



Hi Mom  
======================================================================

About
======================================================================
    
    
#### __Add Study Title Here__
__________________________   


__Status__:	Activated   
__First Enrollment Date:__ `r #add r code here` 

__Projected Number of Patients__:	  
__Current Accrual__: `r n_distinct(mydata$id)`


<hr>
    
#### Purpose of Study     
Blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah blah  


    
 
    
Cohort
======================================================================
    
    
Inputs {.sidebar data-width=310}
---------------------------------------  
<!-- <p style="font-size:70%; color:red;">Dashboard updated: `r format(Sys.time(), '%d %B %Y')`</p>   -->
    
__Dashboard last updated on... __   

<hr>    
    
__Filters__   
```{r}

#---------------- Insert Shiny Filters ----------------------
# examples can be in the Shiny section at https://rmarkdown.rstudio.com/flexdashboard/shiny.html#using_shiny

# 2 examples

# Site
selectInput("site", 
            label = "Mayo site",
            choices = c("All","ARZ","RST","FLA"), 
            selected = "All")

# Gender (without an "all" option)
radioButtons("gender", 
             label = "Gender", 
             choices = c("Male", "Female"), 
             selected = NULL,
             inline = TRUE, 
             width = NULL, 
             choiceNames = NULL,
             choiceValues = NULL)


```


    
Row  
-----------------------------------------------------------------------  
    
### <strong>Overall Accrual</strong>
```{r}
#########################################################################
#### Gauges - Enrollment counts                                   #######
#########################################################################
# Enrollment counts for all sites
renderGauge({

  #filter using gender variable  
  all_count <- if (input$site == "All") n_distinct(mydata$id[mydata$gender == input$gender]) 
               else n_distinct(mydata$id[mydata$site == input$site & mydata$gender == input$gender])  
  
  gauge(all_count,  
      min = 0, # min value on gauge
      max = 10, # max value on gauge
      abbreviate = FALSE, #Abbreviate large numbers for min, max, and value (e.g. 1234567 -> 1.23M)
      sectors = gaugeSectors(success = c(0, 10), # set range and color update when in range
                             colors = c("#373F51")))
})
```

### Arizona
```{r}

renderGauge({
  
  gauge(n_distinct(mydata$id[mydata$gender == input$gender & mydata$site == "ARZ"]), 
      min = 0, 
      max = 5, #target accrual for ARZ
      abbreviate = FALSE,
      sectors = gaugeSectors(success = c(0, 60),
                             colors = c("#A9BCD0")))
})
```

### Florida
```{r}
renderGauge({
  
  gauge(n_distinct(mydata$id[mydata$gender == input$gender & mydata$site == "FLA"]),
      min = 0, 
      max = 60, 
      abbreviate = FALSE,
      sectors = gaugeSectors(success = c(0, 60),
                             colors = c("#A9BCD0")))
})
```

### Rochester
```{r}
renderGauge(

  gauge(n_distinct(mydata$id[mydata$gender == input$gender & mydata$site == "RST"]),
      min = 0, 
      max = 60, 
      abbreviate = FALSE,
      sectors = gaugeSectors(success = c(0, 60),
                             colors = c("#A9BCD0")))
)
```

### Bob
```{r}

```

Row  
-----------------------------------------------------------------------  
    
### Accrual Table {data-width=40}
```{r, echo=FALSE}
renderTable({
  
  select_site <- if (input$site == "All") c("ARZ", "FLA", "RST") else input$site
  
  mydata %>% 
    filter(site %in% select_site,
           gender == input$gender) %>% 
    data.table::data.table()
  
})

```






<!-- ----------------------------------------------------------------------------------- -->
<!-- ----------------------------------------------------------------------------------- -->
<!-- CSS - Control colors / style -->

<style>                     
.navbar-inverse {
    background-color: #ffffff; /******** navbar background color*/
        border-color: #282828; /******** navbar border color*/
}

.navbar-inverse .navbar-brand {
    color: #000000;
}

.navbar-inverse .navbar-brand:hover,
.navbar-inverse .navbar-brand:focus {
    color:  #0d0d0d;
        background-color: transparent;
}

.navbar-inverse .navbar-text {
    color: #777;
}

.navbar-inverse .navbar-nav > li > a {
    color: #777;
}

.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
    color: #0d0d0d;
        background-color: transparent;
}

.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
    color: #555;
        background-color: #FFFFFF;   /********* tab background color*/
}

body {
    padding-top: 60px;
    background: #ffffff;  /********* body background color*/
}

.section.sidebar {
    top: 51px;
    
/* background-color: #f5f5f5; */
    background-color: #ffffff;  /********* sidebar background color*/
    border-color: transparent;  
}

.value-box {
    color: #ffffff;     /********* valuebox text color*/
}

.bg-primary {
    background-color: #16314b; /********* valuebox background color*/
}

</style>
    