---
title: "Dashboard Project Name Here" 
output:
  flexdashboard::flex_dashboard:
    orientation: rows
runtime: shiny
---
    
    
```{r setup, include=FALSE, warning=FALSE}

# Flexdashboard documentation--- https://rmarkdown.rstudio.com/flexdashboard/index.html

# This template is setup to include interactive Shiny elements. Examples can be in the Shiny section at https://rmarkdown.rstudio.com/flexdashboard/shiny.html#using_shiny



#------------------------------ Load Packages ----------------------------------------
library(flexdashboard)
library(plotly)
library(tidyverse)
library(readxl)
library(knitr)
library(kableExtra)
library(shiny)
library(DT)
library(formattable)

```


```{r data, include=FALSE}

#---------------------------------- Data Import ----------------------------------------
data_import <- read_xlsx("../data/isoqol_data.xlsx")



#---------------------------------- Data Transformations --------------------------------
data <- data_import %>% 
  mutate(tx_start_dt = as.Date(tx_start_dt), 
         tx_end_dt = as.Date(tx_end_dt),
         enroll_dt = as.Date(enroll_dt))   
  
# Additional code here


```


About
======================================================================
    
    
#### __Add Study Title Here__  


__Status__:	Activated   
__First Enrollment Date:__ 01/04/2022 

__Projected Number of Patients__:	75  
__Current Accrual__: `r n_distinct(data$case)`


<hr>
    
#### Purpose of Study     
This is a great place to describe your study or copy and paste key information straight from the study protocol.


    

Cohort  
======================================================================  

Inputs {.sidebar}   
---------------------------------------   
 
<hr>    
    
__Use filters below to subset cohort based on their enrollment date.__  

```{r}

#---------------- Insert Shiny Filters ----------------------

# Filter by Enrollment Date

# Stor min and max dates as objects
min_enroll <- min(data$enroll_dt)
max_enroll <- max(data$enroll_dt)

sliderInput(inputId = "enroll_date",
            label = "Enrollment Date", 
            min = min_enroll,
            max = max_enroll,value = c(min_enroll, max_enroll))
```

Row  {data-height="200"}  
-----------------------------------------------------------------------  

### __Overall Accrual__

```{r}
#---- Enrollment counts for all arms

 # Count the number of distinct IDs

renderValueBox({
  overall_n <- n_distinct(data$case[data$enroll_dt >= input$enroll_date[1] &
                                    data$enroll_dt <= input$enroll_date[2]])  
  valueBox(value = overall_n,
         caption = "Overall Accrual", 
         color = "#004c6d")
})
```

### Arm 1

```{r, message=FALSE, echo=FALSE}
#---- Arm 1 enrollment  

renderValueBox({
# filter for Arm 1 cases only
# Count the number of distinct IDs
arm1_n <- data %>% filter(arm == "A: IFL",
                          enroll_dt >= input$enroll_date[1],
                          enroll_dt <= input$enroll_date[2]) %>% with(n_distinct(case))
# Create Value box
valueBox(value = arm1_n, 
         caption = "A: IFL", 
         color = "#9dc6e0")
})

```

### Arm 2

```{r}
#---- Arm 2 enrollment  

renderValueBox({
# filter for Arm 2 cases only
# Count the number of distinct IDs
arm2_n <- data %>% filter(arm == "F: FOLFOX",
                          enroll_dt >= input$enroll_date[1],
                          enroll_dt <= input$enroll_date[2]) %>% with(n_distinct(case))
# Create Value box
valueBox(value = arm2_n, 
         caption = "F: FOLFOX", 
         color = "#9dc6e0")
})

```

### Arm 3

```{r}
#---- Arm 3 enrollment

renderValueBox({
# filter for Arm 3 cases only
# Count the number of distinct IDs
arm3_n <- data %>% filter(arm == "G: IROX",
                          enroll_dt >= input$enroll_date[1],
                          enroll_dt <= input$enroll_date[2]) %>% with(n_distinct(case))

# Create Value box
valueBox(value = arm3_n, 
         caption = "G: IROX", 
         color = "#9dc6e0")
})

```


Row {data-height="800"}
-----------------------------------------------------------------------  

### Enrollment by Sex {data-width="500"}  
```{r, echo=FALSE}
renderPlotly({
  
plot_data <- data %>% filter(enroll_dt >= input$enroll_date[1],
                enroll_dt <= input$enroll_date[2])
ggplotly(ggplot(plot_data,aes(x=sex)) + 
           geom_bar(stat="count",fill="#004c6d") +
           ylab("Count") +
           xlab("Sex") +
           theme_minimal())
})

```

### Enrollment by Age {data-width="500"}  
```{r, echo=FALSE}

renderPlotly({
  plot_data <- data %>% filter(enroll_dt >= input$enroll_date[1],
                  enroll_dt <= input$enroll_date[2])
  
 ggplotly(ggplot(plot_data, aes(x=arm, y=age,fill=arm)) +
            geom_boxplot() + 
            scale_fill_manual(values = c("#003f5c","#bc5090","#ffa600")) +
            theme_bw() + 
            ylab("Age at Enrollment (yrs)") +
            xlab("Treatment Arm") +
            labs(fill = "Arm") +
            theme())
  
})

```


Surveys  
======================================================================

Row  {data-height="200"}
-----------------------------------------------------------------------  

### __Baseline Completion__
```{r}
 # Count the number of distinct IDs
baseline <- data %>% filter(bsl == "Complete")          
baseline_n <- length(unique(baseline$case))

gauge(value = baseline_n,
      min = 0, 
      max = length(unique(data$case)), 
      label = "Baseline Survey",
      gaugeSectors(success = c(0, length(unique(data$case)))))

```

### __Month 3 Completion__
```{r}
 # Count the number of distinct IDs
mo3 <- data %>% filter(mo3 == "Complete")               
mo3_n <- length(unique(mo3$case))

gauge(value = mo3_n,
      min = 0, 
      max = length(unique(data$case)), 
      label = "Month 3",
      gaugeSectors(success = c(60, length(unique(data$case))), 
                   warning = c(40, 59), 
                   danger = c(0, 39)))

```

### __Month 6 Completion__
```{r}
 # Count the number of distinct IDs
mo6 <- data %>% filter(mo6 == "Complete")  %>% count(case)                
mo6_n <- length(unique(mo6$case))
gauge(value = mo6_n,
      min = 0, 
      max = length(unique(data$case)), 
      label = "Month 6",
      gaugeSectors(success = c(60, length(unique(data$case))), 
                   warning = c(40, 59), 
                   danger = c(0, 39)))

```



Row  {data-height="800"}  
-----------------------------------------------------------------------  

### Survey Completion Table

```{r, echo=FALSE, context="server"}
#------- Survey Completion  

# Select the columns we want to show in our table
survey_table <- data %>% select(case, arm, tx_start_dt, tx_end_dt, bsl, mo3, mo6)

as.datatable(formattable(survey_table, list(
  bsl = formatter("span", style = x ~ ifelse(x %in% c("Complete"), 
                                               style(color = "green", 
                                               font.weight = "bold"), 
                                                  ifelse(x %in% c("Overdue"),
                                                        style(color = "#d35e60", 
                                                        font.weight = "bold"), 
                                                  ifelse(x == "Waiting Treatment", 
                                                         style(color = "#FFAA00", 
                                                               font.weight = "bold"), NA))),
                     ~ icontext(sapply(bsl, function(x) if (x %in% c("Complete")) "ok" 
                                       else if (x %in% c("Overdue")) "remove"
                                       else if (x == "Waiting Treatment") "alert" else ""), bsl)),
    mo3 = formatter("span", style = x ~ ifelse(x %in% c("Complete"), 
                                               style(color = "green", 
                                               font.weight = "bold"), 
                                                  ifelse(x %in% c("Overdue"),
                                                        style(color = "#d35e60", 
                                                        font.weight = "bold"), 
                                                  ifelse(x == "Waiting Treatment", 
                                                         style(color = "#FFAA00", 
                                                               font.weight = "bold"), NA))),
                     ~ icontext(sapply(mo3, function(x) if (x %in% c("Complete")) "ok" 
                                       else if (x %in% c("Overdue")) "remove"
                                       else if (x == "Waiting Treatment") "alert" else ""), mo3)),
      mo6 = formatter("span", style = x ~ ifelse(x %in% c("Complete"), 
                                               style(color = "green", 
                                               font.weight = "bold"), 
                                                  ifelse(x %in% c("Overdue"),
                                                        style(color = "#d35e60", 
                                                        font.weight = "bold"), 
                                                  ifelse(x == "Waiting Treatment", 
                                                         style(color = "#FFAA00", 
                                                               font.weight = "bold"), NA))),
                     ~ icontext(sapply(mo6, function(x) if (x %in% c("Complete")) "ok" 
                                       else if (x %in% c("Overdue")) "remove"
                                       else if (x == "Waiting Treatment") "alert" else ""), mo6)))),
  colnames = c("Case" = "case",
               "Treatment Arm" = "arm",
               "Treatment Start" = "tx_start_dt",
               "Treatment End" = "tx_end_dt",
               "Baseline Survey" = "bsl",
               "Month 3" = "mo3",
               "Month 6" = "mo6"),
  extensions = 'Buttons',
  rownames = T,
  filter = list(
    position = 'top', clear = FALSE, plain = TRUE),
  options = list(dom = 'Bfrtip',
                 buttons = list(
                   list(extend = "excel", text = "Download Table", filename = "export",
                        exportOptions = list(
                          modifier = list(page = "all"),
                          orthogonal = "export"))),
                 pageLength = nrow(survey_table)))

```





<!-- ----------------------------------------------------------------------------------- -->
<!-- ----------------------------------------------------------------------------------- -->
<!-- CSS - Control colors / style -->

<style>                     
.navbar-inverse {
    background-color: #ffffff; /******** navbar background color*/
        border-color: #282828; /******** navbar border color*/
}

.navbar-inverse .navbar-brand {
    color: #000000;
}

.navbar-inverse .navbar-brand:hover,
.navbar-inverse .navbar-brand:focus {
    color:  #0d0d0d;
        background-color: transparent;
}

.navbar-inverse .navbar-text {
    color: #777;
}

.navbar-inverse .navbar-nav > li > a {
    color: #777;
}

.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
    color: #0d0d0d;
        background-color: transparent;
}

.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
    color: #555;
        background-color: #FFFFFF;   /********* tab background color*/
}

body {
    padding-top: 60px;
    background: #ffffff;  /********* body background color*/
}

.section.sidebar {
    top: 51px;
    
/* background-color: #f5f5f5; */
    background-color: #ffffff;  /********* sidebar background color*/
    border-color: transparent;  
}

.value-box {
    color: #ffffff;     /********* valuebox text color*/
}

.bg-primary {
    background-color: #16314b; /********* valuebox background color*/
}

</style>
    